---
title: "&nbsp;"
output:
  html_document:
    toc_float: false
    self_contained: false
    includes:
       in_header: lightbox.html
---
<style>
.GFG {
background-color: white;
border: 2px solid black;
color: green;
padding: 5px 10px;
text-align: center;
display: inline-block;
font-size: 20px;
margin: 10px 30px;
cursor: pointer;
}
.back {
background-color: grey;
border: 2px solid black;
color: black;
padding: 5px 10px;
text-align: center;
display: inline-block;
font-size: 12px;
margin: 10px 30px;
cursor: pointer;
}
<!-- .button { -->
<!--     position: relative; -->
<!--     margin: 0px 0px 38px calc((100% - 980px) * 0.5); -->
<!--     left: 34px; -->
<!--     grid-area: 3 / 1 / 4 / 2; -->
<!--     justify-self: start; -->
<!--     align-self: start; -->
<!-- } -->
</style>

```{r setup, include=FALSE}
##setting code chunks for rest ofz sections no code being shown, and no messages.
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, error = FALSE )
```

```{r libraries}
library(htmltools)
library(bsplus)
library(magrittr)
```

## HERUS People

### Head of Laboratory

```{r button1}

br()
div(class = "button",
a(href="#", `data-featherlight`="#claudia",
  bs_button("Professor Claudia R. Binder")),

div(class = "lightbox",
    id = "claudia",
    img(src = "https://people.epfl.ch/private/common/photos/links/265222.jpg?ts=1660131999"),
    h3("Professor Claudia Binder"),
    a(href = "https://people.epfl.ch/claudia.binder?lang=en", "more info"))
)
```

### Scientists

```{r button2}
br()
div(class = "button",
a(href="#", `data-featherlight`="#Aristide",
  bs_button("Dr. Aristide Athanassiadis")),

div(class = "lightbox",
    id = "Aristide",
    img(src = "https://people.epfl.ch/private/common/photos/links/326088.jpg?ts=1660132148"),
    h3("Dr. Aristide Athanassiadis"),
    a(href = "https://people.epfl.ch/aristide.athanassiadis?lang=en", "more info")),

a(href="#", `data-featherlight`="#Mert",
  bs_button("Dr. Mert Duygan")),

div(class = "lightbox",
    id = "Mert",
    img(src = "https://people.epfl.ch/private/common/photos/links/348065.jpg?ts=1660132195"),
    h3("Dr. Mert Duygan"),
    a(href = "https://people.epfl.ch/mert.duygan?lang=en", "more info")),
br(),
br(),

a(href="#", `data-featherlight`="#Maria",
  bs_button("Dr. Maria Hecher")),

div(class = "lightbox",
    id = "Maria",
    img(src = "https://people.epfl.ch/private/common/photos/links/324531.jpg?ts=1660132985"),
    h3("Dr. Maria Hecher"),
    a(href = "https://people.epfl.ch/maria.hecher?lang=en", "more info")),

a(href="#", `data-featherlight`="#Silvia",
  bs_button("Dr. Silvia Hostettler")),

div(class = "lightbox",
    id = "Silvia",
    img(src = "https://people.epfl.ch/private/common/photos/links/118273.jpg?ts=1660132986"),
    h3("Dr. Silvia Hostettler"),
    a(href = "https://people.epfl.ch/silvia.hostettler?lang=en", "more info"))
)
br()
div( class ="button",
a(href="#", `data-featherlight`="#Susan",
  bs_button("Dr. Susan Mühlemeier")),
div(class = "lightbox",
    id = "Susan",
    img(src = "https://people.epfl.ch/private/common/photos/links/267683.jpg?ts=1660132989"),
    h3("Dr. Susan Mühlemeier"),
    a(href = "https://people.epfl.ch/susan.muhlemeier?lang=en", "more info")),

a(href="#", `data-featherlight`="#Catarina",
  bs_button("Dr. Catarina Wall Gago")),
div(class = "lightbox",
    id = "Catarina",
    img(src = "https://people.epfl.ch/private/common/photos/links/169929.jpg?ts=1660132990"),
    h3("Dr. Catarina Wall Gago"),
    a(href = "https://people.epfl.ch/catarina.wall?lang=en", "more info"))
)
```


### Doctoral Assistants

```{r button8}
br()
div(class = "button",
    
a(href="#", `data-featherlight`="#Matteo",
  bs_button("Matteo Barsanti")),
div(class = "lightbox",
    id = "Matteo",
    img(src = "https://people.epfl.ch/private/common/photos/links/318435.jpg?ts=1660133276"),
    h3("Matteo Barsanti"),
    a(href = "https://people.epfl.ch/matteo.barsanti?lang=en", "more info")),

a(href="#", `data-featherlight`="#Anne",
  bs_button("Anne Bösch")),
div(class = "lightbox",
    id = "Anne",
    img(src = "https://people.epfl.ch/private/common/photos/links/162616.jpg?ts=1660133279"),
    h3("Anne Bösch"),
    a(href = "https://people.epfl.ch/anne.boesch?lang=en", "more info")),
br(),
br(),
a(href="#", `data-featherlight`="#Gloria",
  bs_button("Gloria Serra Coch")),
div(class = "lightbox",
    id = "Gloria",
    img(src = "https://people.epfl.ch/private/common/photos/links/274178.jpg?ts=1660133282"),
    h3("Gloria Serra Coch"),
    a(href = "https://people.epfl.ch/gloria.serracoch?lang=en", "more info")),

a(href="#", `data-featherlight`="#Giulia",
  bs_button("Giulia Frigo")),

div(class = "lightbox",
    id = "Giulia",
    img(src = "https://people.epfl.ch/private/common/photos/links/332385.jpg?ts=1660133286"),
    h3("Giulia Frigo"),
    a(href = "https://people.epfl.ch/giulia.frigo?lang=en", "more info"))
)
br()
div(class = "button",
a(href="#", `data-featherlight`="#Melissa",
  bs_button("Melissa Pang")),
div(class = "lightbox",
    id = "Melissa",
    img(src = "https://people.epfl.ch/private/common/photos/links/255185.jpg?ts=1660133289"),
    h3("Melissa Pang"),
    a(href = "https://people.epfl.ch/melissa.pang?lang=en", "more info")),

a(href="#", `data-featherlight`="#Kaz",
  bs_button("Kaz Sakamoto")),
div(class = "lightbox",
    id = "Kaz",
    img(src = "https://people.epfl.ch/private/common/photos/links/348070.jpg?ts=1660133290"),
    h3("Kaz Sakamoto"),
    a(href = "https://people.epfl.ch/kazuki.sakamoto?lang=en", "more info")),

a(href="#", `data-featherlight`="#Ankita",
  bs_button("Ankita Singhvi")),
div(class = "lightbox",
    id = "Ankita",
    img(src = "https://people.epfl.ch/private/common/photos/links/348099.jpg?ts=1660133293"),
    h3("Ankita Singhvi"),
    a(href = "https://people.epfl.ch/ankita.singhvi?lang=en", "more info"))
)

br()
```
<div class = "button">
<a href='choices.html'>
<button class="btn btn-secondary">back</button>
</a>
</div>